{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2019-02-08 papers/methods/paper.tex
Removing p

\begin{align}
&P({\rm data}|\theta) \propto \notag \\
&\int\, d\mu\, dm_B\, dx_1\, dc\, dz, dm \  P(\hat{z}|z) P(\hat{m}|m)  \notag \\
& P(\hat{m}_B, \hat{x}_1, \hat{c}, \hat{\mathcal{C}}_\eta^{-1} | m_B, x_1, c, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) \notag \\
& P(x_1, c |  \langle x_1^i \rangle, \langle c^i \rangle, \sigma_{x_1}, \sigma_c, z) \notag\\
& P(m_B | \langle M_B \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta, z, m, p) \notag \\
& P(\mu |z, \Omega_m, w).
\end{align}

>>>>

\begin{align}
&P({\rm data}|\theta) \propto \notag \\
&\int\, d\mu\, dm_B\, dx_1\, dc\, dz, dm \  P(\hat{z}|z) P(\hat{m}|m)  \notag \\
& P(\hat{m}_B, \hat{x}_1, \hat{c}, \hat{\mathcal{C}}_\eta^{-1} | m_B, x_1, c, \delta \mathcal{Z}_i, \kappa_0, \kappa_1) \notag \\
& P(x_1, c |  \langle x_1^i \rangle, \langle c^i \rangle, \sigma_{x_1}, \sigma_c, z) \notag\\
& P(m_B | \langle M_B \rangle, \mu, \delta(0), \delta(\infty), \sigma_{M_B}, \sigma_{x_1}, \sigma_c, \alpha, \beta, z, m) \notag \\
& P(\mu |z, \Omega_m, w).
\end{align}
